---
title: "Aquatic Ecosystems - Lakes Section: Heat Fluxes Analysis"
author: "Damien Bouffard"
date: "2026"
output:
  html_document:
    toc: true
    toc_float: true
    theme: "flatly"
---

# Limnolab

## Goal

The goal of this LimnoLab is to quantify (i) **the importance of the riverine throughflow heat transport compared to the atmospheric heat fluxes** and (ii) **how this contribution might change with the connection between Lake Schiffenen and Lake Morat**.

Specifically we propose to:

1. Estimate the heat fluxes (atmospheric and throughflow) over the period 1981 - 2022
2. Estimate the relative importance of the throughflow for the period 1981 - 2022 and possible future connection between Lake Schiffenen and Lake Morat (using period 1981 - 2022 with an increased discharge into Lake Morat)

## (Proposed) Method

1. Provide a schematic of the problem including heat sources and sinks that illustrate the research question
2. Prepare the dataset (this part is partly provided in this RMarkdown)
3. Estimate the atmospheric heat flux (codes are provided)
4. Estimate the river throughflow heat flux (codes are provided)
5. Run the same calculation in case of a future connection between Schiffenen and Morat
6. Evaluate the current contribution of the throughflow on the heat budget
7. Evaluate the future contribution of Lake Schiffenen on the heat budget
8. Discuss the role of the throughflow. You may consider the change in water residence time between the two scenario

## Code

This LimnoLab is provided with R support in this RMarkdown document. The code is commented extensively to make it easy for non-expert R users.

---

# R scripts

## Lake Morat properties

```{r}
Volume_Morat <- 0.55 * 1e9  # [m3]
Surf_area <- 22.8 * 1e6     # [m2]
```

# Part 0. Import the libraries

```{r setup, include=FALSE}
# Install packages if needed
packages <- c("tidyverse", "readr", "lubridate", "ggplot2", "gridExtra")
new_packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new_packages)) install.packages(new_packages)

# Load libraries
library(tidyverse)
library(readr)
library(lubridate)
library(ggplot2)
library(gridExtra)

# Set plot theme
theme_set(theme_minimal() + theme(text = element_text(size = 12)))
```

## Source the heat fluxes functions

The heat flux functions will be sourced from the heat_fluxes_lakes_R.R file.

```{r}
# Load the heat flux functions
source('heat_fluxes_lakes_R.R')
```

---

# Part 1. Load Meteorological data

Data from the meteorological station from Neuchâtel (MeteoSwiss NEU) can be found here:

> ../data/ForcingMorat.dat

**Comments:** 'ForcingMorat.dat' is an ASCII file (e.g. a text file) that can be opened by all text or data editors. The first line is the header and indicates the content of the different columns:

- **Time_[d]**: Time is in days since 01.01.1981. 
- **u_[m/s]**: Wind velocity in East direction. Units [m/s]
- **v_[m/s]**: Wind velocity in North direction. Units [m/s]
- **Tair_[°C]**: Air temperature. Units [°C]
- **sol_[W/m2]**: Net solar radiation. Units [W/m²]
- **vap_[mbar]**: Water vapor pressure. Units [mbar]
- **cloud_[-]**: Cloud coverage. No units. 0 = cloud free; 1 = sky fully covered by clouds
- **rain_[m/hr]**: Precipitation. Units [m/h]

## Load forcing data

```{r}
# Load the meteorological data
mydir <- '../data/'
myfile <- 'ForcingMorat.dat'

# Create a data frame
df <- read_delim(file.path(mydir, myfile), delim = ' ', col_types = cols())

# Print the first few lines
head(df)
```

## Set the index as time

```{r}
# Start of the time series on 01.01.1981 00:00:00
date_ref <- ymd('1981-01-01')

# Create a time vector
df <- df %>%
  mutate(time = date_ref + days(`Time_[d]`)) %>%
  mutate(time = floor_date(time, unit = 'hour'))  # Round to hour

# Print the first few lines
head(df)
```

## Convert North and East winds into wind speed and drop unused columns

$U_{10} = \sqrt{u^2 + v^2}$

```{r}
df <- df %>%
  mutate(U10_[m/s] = sqrt(`u_[m/s]`^2 + `v_[m/s]`^2)) %>%
  select(-`u_[m/s]`, -`v_[m/s]`, -`Time_[d]`)

head(df)
```

## Select period

Ideally start with a one-year period to validate your codes, then the final analysis could be run over the full time window.

```{r}
start_day <- ymd('2010-01-01')
end_day <- ymd('2010-12-31')
```

## Display meteorological forcing

- Air temperature
- Wind speed
- Solar radiation

```{r, fig.width=8, fig.height=8}
# Filter data for selected period
df_period <- df %>%
  filter(time >= start_day & time <= end_day)

# Calculate daily means
df_daily <- df_period %>%
  mutate(date = date(time)) %>%
  group_by(date) %>%
  summarise(
    Tair_mean = mean(`Tair_[°C]`),
    U10_mean = mean(`U10_[m/s]`),
    sol_mean = mean(`sol_[W/m2]`)
  )

# Create plots
p1 <- ggplot(df_period, aes(x = time, y = `Tair_[°C]`)) +
  geom_line(alpha = 0.5) +
  geom_line(data = df_daily %>% mutate(time = as_datetime(date)), 
            aes(y = Tair_mean), color = 'red', linewidth = 1) +
  labs(y = 'Air Temperature (°C)', x = '') +
  theme(axis.text.x = element_blank())

p2 <- ggplot(df_period, aes(x = time, y = `U10_[m/s]`)) +
  geom_line(alpha = 0.5) +
  geom_line(data = df_daily %>% mutate(time = as_datetime(date)), 
            aes(y = U10_mean), color = 'red', linewidth = 1) +
  labs(y = 'Wind Speed (m/s)', x = '') +
  theme(axis.text.x = element_blank())

p3 <- ggplot(df_period, aes(x = time, y = `sol_[W/m2]`)) +
  geom_line(alpha = 0.5) +
  geom_line(data = df_daily %>% mutate(time = as_datetime(date)), 
            aes(y = sol_mean), color = 'red', linewidth = 1) +
  labs(y = 'Solar Radiation (W/m²)', x = 'Time')

grid.arrange(p1, p2, p3, ncol = 1)
```

Make sure that the figures are consistent with your expectations.

---

# Part 2. Load Lake Temperature data

The lake temperature data provided here are already the output of a 1D hydrodynamic model (Simstrat):

> ../data/Results/T_out.dat

Cantonal monitoring data can be found here:

> ../data/Temperature_Morat.csv

They can be used to compare with the model but this is not a requirement here.

## Load lake temperature data

```{r}
# Load the lake temperature data
mydir <- '../data/Results/'
myfile <- 'T_out.dat'

# Create a data frame
df_T <- read_delim(file.path(mydir, myfile), delim = ' ', col_types = cols())

head(df_T)
```

**Description:**

The first column indicates the time in days. The following columns indicate the lake temperature at preselected depths, here every 1 m starting from the bottom = -45.000 to the surface = -0.000

## Set time as index and extract surface temperature

```{r}
# Set time as index
date_ref <- ymd('1981-01-01')

df_T <- df_T %>%
  mutate(time = date_ref + days(Datetime)) %>%
  mutate(doy = yday(time)) %>%
  select(time, doy, everything(), -Datetime)

# Extract surface temperature only
df_Morat <- df_T %>%
  select(time, `Temp_[C]` = `-0.000`)

head(df_Morat)
```

## Plot the surface temperature

```{r, fig.width=8, fig.height=4}
df_Morat_period <- df_Morat %>%
  filter(time >= start_day & time <= end_day)

ggplot(df_Morat_period, aes(x = time, y = `Temp_[C]`)) +
  geom_line() +
  labs(y = 'Surface Temperature (°C)', x = 'Time') +
  theme_minimal()
```

---

# Part 3. Merge the 2 datasets (meteorological and lake temperature data)

```{r}
# Merge the datasets
df_all <- df %>%
  left_join(df_Morat, by = 'time') %>%
  fill(Temp_[C], .direction = 'down')

head(df_all)
```

## Add lake surface temperature to the plot

```{r, fig.width=8, fig.height=8}
df_all_period <- df_all %>%
  filter(time >= start_day & time <= end_day)

# Calculate weekly means
df_weekly <- df_all_period %>%
  mutate(week = floor_date(time, unit = 'week')) %>%
  group_by(week) %>%
  summarise(
    Tair_mean = mean(`Tair_[°C]`),
    U10_mean = mean(`U10_[m/s]`),
    sol_mean = mean(`sol_[W/m2]`),
    Temp_mean = mean(`Temp_[C]`, na.rm = TRUE)
  )

p1 <- ggplot(df_all_period, aes(x = time, y = `Tair_[°C]`)) +
  geom_line(alpha = 0.5) +
  geom_line(data = df_weekly %>% mutate(time = week), 
            aes(y = Tair_mean), color = 'red', linewidth = 1) +
  labs(y = 'Air Temperature (°C)', x = '') +
  theme(axis.text.x = element_blank())

p2 <- ggplot(df_all_period, aes(x = time, y = `U10_[m/s]`)) +
  geom_line(alpha = 0.5) +
  geom_line(data = df_weekly %>% mutate(time = week), 
            aes(y = U10_mean), color = 'red', linewidth = 1) +
  labs(y = 'Wind Speed (m/s)', x = '') +
  theme(axis.text.x = element_blank())

p3 <- ggplot(df_all_period, aes(x = time, y = `sol_[W/m2]`)) +
  geom_line(alpha = 0.5) +
  geom_line(data = df_weekly %>% mutate(time = week), 
            aes(y = sol_mean), color = 'red', linewidth = 1) +
  labs(y = 'Solar Radiation (W/m²)', x = '') +
  theme(axis.text.x = element_blank())

p4 <- ggplot(df_all_period, aes(x = time, y = `Temp_[C]`)) +
  geom_line(alpha = 0.5) +
  geom_line(data = df_weekly %>% mutate(time = week), 
            aes(y = Temp_mean), color = 'red', linewidth = 1) +
  labs(y = 'Lake Temperature (°C)', x = 'Time')

grid.arrange(p1, p2, p3, p4, ncol = 1)
```

---

# Part 4. Heat flux functions

The functions to calculate the different terms of the heat fluxes can be found in the source file.

## Direct Albedo

The time-varying direct albedo, *Adir*, is added to the dataframe.

```{r}
# Create a lookup table for albedo by month
albedo_by_month <- tibble(
  month = 1:12,
  Adir = c(0.22, 0.161, 0.108, 0.084, 0.075, 0.073, 0.074, 0.080, 0.099, 0.144, 0.210, 0.241)
)

# Add albedo to the dataframe
df_all <- df_all %>%
  mutate(month = month(time)) %>%
  left_join(albedo_by_month, by = 'month') %>%
  select(-month)

head(df_all)
```

---

# Heat flux calculation

```{r}
# Short-wave absorption
df_all <- df_all %>%
  mutate(H_sw = SW(`sol_[W/m2]`, `cloud_[-]`, Adir))

# Incoming long-wave radiation
df_all <- df_all %>%
  mutate(Ea = emissivity_(`Tair_[°C]`, `vap_[mbar]`, `cloud_[-]`),
         H_lw_in = LW_in(`Tair_[°C]`, Ea))

# Outgoing long-wave radiation
df_all <- df_all %>%
  mutate(H_lw_out = LW_out(`Temp_[C]`))

# Latent heat flux
df_all <- df_all %>%
  mutate(H_le = He(`Tair_[°C]`, `Temp_[C]`, `U10_[m/s]`, `vap_[mbar]`))

# Sensible heat flux
df_all <- df_all %>%
  mutate(H_c = Hc(`Tair_[°C]`, `Temp_[C]`, `U10_[m/s]`))

# Sum of atmospheric heat flux
df_all <- df_all %>%
  mutate(H_net_atm = H_sw + H_lw_in + H_lw_out + H_le + H_c)

head(df_all)
```

## Plot of atmospheric heat fluxes

```{r, fig.width=6, fig.height=5}
df_all_period_month <- df_all %>%
  mutate(month = month(time)) %>%
  group_by(month) %>%
  summarise(
    H_sw_mean = mean(H_sw, na.rm = TRUE),
    H_sw_sd = sd(H_sw, na.rm = TRUE),
    H_lw_in_mean = mean(H_lw_in, na.rm = TRUE),
    H_lw_in_sd = sd(H_lw_in, na.rm = TRUE),
    H_lw_out_mean = mean(H_lw_out, na.rm = TRUE),
    H_lw_out_sd = sd(H_lw_out, na.rm = TRUE),
    H_le_mean = mean(H_le, na.rm = TRUE),
    H_le_sd = sd(H_le, na.rm = TRUE),
    H_c_mean = mean(H_c, na.rm = TRUE),
    H_c_sd = sd(H_c, na.rm = TRUE),
    H_net_atm_mean = mean(H_net_atm, na.rm = TRUE),
    H_net_atm_sd = sd(H_net_atm, na.rm = TRUE)
  ) %>%
  pivot_longer(-month, names_to = c('Flux', '.value'), names_sep = '_(?=[^_]+$)')

ggplot(df_all_period_month, aes(x = month, y = mean, color = Flux, linewidth = Flux)) +
  geom_ribbon(aes(ymin = mean - sd, ymax = mean + sd, fill = Flux), alpha = 0.2, color = NA, linewidth = 0, show.legend = FALSE) +
  geom_line() +
  scale_linewidth_manual(values = c('H_net_atm' = 1.5, 'H_sw' = 0.8, 'H_lw_in' = 0.8, 
                                     'H_lw_out' = 0.8, 'H_le' = 0.8, 'H_c' = 0.8)) +
  scale_color_manual(values = c('H_net_atm' = 'black', 'H_sw' = 'orange', 'H_lw_in' = 'red', 
                                 'H_lw_out' = 'blue', 'H_le' = 'green', 'H_c' = 'purple')) +
  scale_fill_manual(values = c('H_net_atm' = 'black', 'H_sw' = 'orange', 'H_lw_in' = 'red', 
                                'H_lw_out' = 'blue', 'H_le' = 'green', 'H_c' = 'purple')) +
  labs(y = 'Heat Fluxes (W/m²)', x = 'Time') +
  theme(legend.position = 'lower left')
```

---

# Part 5. Throughflow

The inflow temperature and discharge data are already formatted as input files for the 1D hydrodynamic model Simstrat.

The discharge data of the inflow can be found here:

> ../data/Qin.dat

The temperature data of the inflow can be found here:

> ../data/Tin.dat

We assume that the discharge of the outflow is equal to the discharge of the inflow.

## Load discharge data

```{r}
mydir <- '../data/'
myfile <- 'Qin.dat'

# Read discharge data (skip first 3 header lines)
df_Qin <- read.table(file.path(mydir, myfile), skip = 3)
colnames(df_Qin) = c('Time_d', 'Q_in_m3s')
# Set time as index
date_ref <- ymd('1981-01-01')
df_Qin <- df_Qin %>%
  mutate(time = date_ref + ddays(Time_d)) %>%
  mutate(time = floor_date(time, unit = 'hour')) %>%
  select(time, Q_in_m3s)

head(df_Qin)
```

## Load inflow temperature data

```{r}
mydir <- '../data/'
myfile <- 'Tin.txt'

# Read temperature data (skip first 3 header lines)
df_Tin <- read.table(file.path(mydir, myfile), skip = 3)
colnames(df_Tin) = c('Time_d', 'T_in_C')
# Set time as index
date_ref <- ymd('1981-01-01')
df_Tin <- df_Tin %>%
  mutate(time = date_ref + ddays(Time_d)) %>%
  mutate(time = floor_date(time, unit = 'hour')) %>%
  select(time, T_in_C)

head(df_Tin)
```

---

# Part 6. Merge the discharge dataset with the previous dataset

```{r}
# Merge discharge and temperature
df_QT <- df_Qin %>%
  left_join(df_Tin, by = "time") %>%
  fill( T_in_C, .direction = 'down')

# Merge all datasets
data <- df_all %>%
  left_join(df_QT, by = 'time') %>%
  fill(Q_in_m3s, T_in_C, .direction = 'down')

# Calculate throughflow heat flux
data <- data %>%
  mutate(H_f = Hf(Q_in_m3s,  T_in_C, Temp_C, Surf_area))

head(data)
```

## Plot of all heat fluxes including throughflow

```{r, fig.width=7, fig.height=5}
data_period <- data %>%
  filter(time >= start_day & time <= end_day)

data_period_month <- data_period %>%
  mutate(month = month(time)) %>%
  group_by(month) %>%
  summarise(
    H_sw = mean(H_sw),
    H_lw_in = mean(H_lw_in),
    H_lw_out = mean(H_lw_out),
    H_le = mean(H_le),
    H_c = mean(H_c),
    H_f = mean(H_f),
    H_net_atm = mean(H_net_atm)
  ) %>%
  pivot_longer(-month, names_to = 'Flux', values_to = 'Value')

ggplot(data_period_month, aes(x = month, y = Value, color = Flux)) +
  geom_line() +
  labs(y = 'Heat Fluxes (W/m²)', x = 'Time') +
  theme(legend.position = 'lower left')
```

---

# Part 7. Analyze the entire dataset (from 1981 to 2022)

```{r}
start_day <- ymd('1981-01-01')
end_day <- ymd('2022-12-31')

data <- data %>%
  mutate(doy = yday(time))
```

## Daily average heat fluxes by day of year

```{r, fig.width=7, fig.height=5}
data_analysis <- data %>%
  filter(time >= start_day & time <= end_day)

data_doy <- data_analysis %>%
  group_by(doy) %>%
  summarise(
    H_sw = mean(H_sw, na.rm = TRUE),
    H_lw_in = mean(H_lw_in, na.rm = TRUE),
    H_lw_out = mean(H_lw_out, na.rm = TRUE),
    H_le = mean(H_le, na.rm = TRUE),
    H_c = mean(H_c, na.rm = TRUE),
    H_f = mean(H_f, na.rm = TRUE),
    H_net_atm = mean(H_net_atm, na.rm = TRUE)
  ) %>%
  pivot_longer(-doy, names_to = 'Flux', values_to = 'Value')

ggplot(data_doy, aes(x = doy, y = Value, color = Flux)) +
  geom_line() +
  labs(y = 'Heat Fluxes (W/m²)', x = 'Day of Year') +
  theme(legend.position = 'lower left')
```

## Heat fluxes with variability (mean ± std)

```{r, fig.width=7, fig.height=5}
data_doy_stats <- data_analysis %>%
  group_by(doy) %>%
  summarise(
    H_sw_mean = mean(H_sw, na.rm = TRUE),
    H_sw_std = sd(H_sw, na.rm = TRUE),
    H_lw_in_mean = mean(H_lw_in, na.rm = TRUE),
    H_lw_in_std = sd(H_lw_in, na.rm = TRUE),
    H_lw_out_mean = mean(H_lw_out, na.rm = TRUE),
    H_lw_out_std = sd(H_lw_out, na.rm = TRUE),
    H_le_mean = mean(H_le, na.rm = TRUE),
    H_le_std = sd(H_le, na.rm = TRUE),
    H_c_mean = mean(H_c, na.rm = TRUE),
    H_c_std = sd(H_c, na.rm = TRUE),
    H_f_mean = mean(H_f, na.rm = TRUE),
    H_f_std = sd(H_f, na.rm = TRUE),
    H_net_atm_mean = mean(H_net_atm, na.rm = TRUE)
  )

ggplot() +
  # H_sw
  geom_line(data = data_doy_stats, aes(x = doy, y = H_sw_mean, color = 'H_sw'), linewidth = 0.8) +
  geom_ribbon(data = data_doy_stats, aes(x = doy, ymin = H_sw_mean - H_sw_std, 
                                         ymax = H_sw_mean + H_sw_std), alpha = 0.2, fill = 'orange') +
  # H_lw_in
  geom_line(data = data_doy_stats, aes(x = doy, y = H_lw_in_mean, color = 'H_lw_in'), linewidth = 0.8) +
  geom_ribbon(data = data_doy_stats, aes(x = doy, ymin = H_lw_in_mean - H_lw_in_std, 
                                         ymax = H_lw_in_mean + H_lw_in_std), alpha = 0.2, fill = 'red') +
  # H_lw_out
  geom_line(data = data_doy_stats, aes(x = doy, y = H_lw_out_mean, color = 'H_lw_out'), linewidth = 0.8) +
  geom_ribbon(data = data_doy_stats, aes(x = doy, ymin = H_lw_out_mean - H_lw_out_std, 
                                         ymax = H_lw_out_mean + H_lw_out_std), alpha = 0.2, fill = 'blue') +
  # H_le
  geom_line(data = data_doy_stats, aes(x = doy, y = H_le_mean, color = 'H_le'), linewidth = 0.8) +
  geom_ribbon(data = data_doy_stats, aes(x = doy, ymin = H_le_mean - H_le_std, 
                                         ymax = H_le_mean + H_le_std), alpha = 0.2, fill = 'green') +
  # H_c
  geom_line(data = data_doy_stats, aes(x = doy, y = H_c_mean, color = 'H_c'), linewidth = 0.8) +
  geom_ribbon(data = data_doy_stats, aes(x = doy, ymin = H_c_mean - H_c_std, 
                                         ymax = H_c_mean + H_c_std), alpha = 0.2, fill = 'purple') +
  # H_f
  geom_line(data = data_doy_stats, aes(x = doy, y = H_f_mean, color = 'H_f'), linewidth = 0.8) +
  geom_ribbon(data = data_doy_stats, aes(x = doy, ymin = H_f_mean - H_f_std, 
                                         ymax = H_f_mean + H_f_std), alpha = 0.2, fill = 'brown') +
  # H_net_atm
  geom_line(data = data_doy_stats, aes(x = doy, y = H_net_atm_mean, color = 'H_net_atm'), linewidth = 1.5) +
  scale_color_manual(values = c('H_sw' = 'orange', 'H_lw_in' = 'red', 'H_lw_out' = 'blue',
                                 'H_le' = 'green', 'H_c' = 'purple', 'H_f' = 'brown', 
                                 'H_net_atm' = 'black')) +
  labs(y = 'Heat Fluxes (W/m²)', x = 'Day of Year', color = 'Flux Type') +
  theme(legend.position = 'top')
```

---

# Part 8. Future scenario: Connection between Lake Schiffenen and Lake Morat

This is now your turn...

## Methods

### Change throughflow

**Hypothesis:** The flow is now constant 30 m³/s and the water is taken from the bottom of Lake Schiffenen. We assume first that the bottom temperature of Lake Schiffenen is constant and equal to 5°C. You can also test other scenarios.

You need to modify:

- The discharge from inflow 'Qin.dat'. The easiest solution is to open this file in a Text Editor or in Excel and change the discharge to a constant value = 30. Save the file as 'Qin_connection.dat'
- The temperature from inflow 'Tin.dat'. The easiest solution is to open this file in a Text Editor or in Excel and change the temperature to a constant value = 5. Save the file as 'Tin_connection.dat'

The next step is to run the script above by changing:
- `myfile <- 'Qin.txt'` to `myfile <- 'Qin_connection.txt'`
- `myfile <- 'Tin.txt'` to `myfile <- 'Tin_connection.txt'`

---

## Results and Discussion

- Discuss how the total heat budget will be modified by this connection between Lake Schiffenen and Lake Morat

- Discuss how the lake temperature of Lake Morat will be affected by this connection between Lake Schiffenen and Lake Morat

- Are the conclusions changing if you extract the water at a shallower depth in Lake Schiffenen - for instance 10 m above the bottom or 20 m above the bottom? Quantify the changes.

- Provide a convincing conclusion using the schematic that you have prepared at the beginning of this LimnoLab. You may use the paper from Raman Vinna et al. (2018) for your discussion.

**References:**

Raman Vinna, L., Wüest, A., Zappa, M., Fink, G., and Bouffard, D.: Tributaries affect the thermal response of lakes to climate change, Hydrol. Earth Syst. Sci., 22, 31–51, https://doi.org/10.5194/hess-22-31-2018, 2018

Other relevant literature:

Fink, G., Schmid, M., Wahl, B., Wolf, T., & Wüest, A. (2014). Heat flux modifications related to climate‐induced warming of large European lakes. Water Resources Research, 50(3), 2072-2085.

Piccolroaz, S., Zhu, S., Ladwig, R., Carrea, L., Oliver, S., Piotrowski, A. P., ... & Zhu, D. Z. (2024). Lake water temperature modeling in an Era of climate change: Data sources, models, and future prospects. Reviews of Geophysics, 62(1), e2023RG000816.

Råman Vinnå, L., Wüest, A., & Bouffard, D. (2017). Physical effects of thermal pollution in lakes. Water Resources Research, 53(5), 3968-3987.

Schmid, M., & Read, J. (2022). Heat budget of lakes. Encyclopedia of Inland Waters, second edition, edited by: Mehner, T. and Tockner, K., Elsevier, 467-473.

---

## Questions

Contact Damien Bouffard damien.bouffard@unil.ch
